What we {\sf eval} in the shadows

### 2021-04-01 paper/main.tex
more

\subsection{The environment of \eval}

The \c{envir} argument of \eval can be an actual environment, but also \c{Null},
a list, a dataframe, a pairlist or even an integer.

Most of the time, \ie in \packageEnvirEnvSitePercent of the sites, \eval is
passed an actual environment. In \packageNbEnvirIncorrectSites sites
(\packageEnvirIncorrectSitePercent), \eval is passed an incorrect argument, for
instance \c{NA}, a boolean, which makes \eval fail.

\c{NULL}, a \c{list} or a data frame, or an integer, happen in
\packageEnvirUnusualSitePercent of the cases: \eval copies the fields of the
list or data frame and creates bindings for them in a new environment. This
pattern is used to evaluate formulas which can directly refer to the fields of
the data. The \c{envir} argument can also be a number $n$. It means that the
environment in which the expressions is evaluated will be the result of
\c{sys.call(n)} where $n$ refers to the $n$-th stack frame.

>>>>

\subsection{The environments of \eval}

The \c{envir} argument of \eval can be an actual environment, but also \c{Null},
a list, a dataframe, a pairlist or even an integer. Most of the time, \ie in
\packageEnvirEnvSitePercent of the sites, \eval is passed an actual environment.
In \packageNbEnvirIncorrectSites sites (\packageEnvirIncorrectSitePercent),
\eval is passed an incorrect argument, for instance \c{NA}, a boolean, which
makes \eval fail. \c{NULL}, a \c{list} or a data frame, or an integer, happen in
\packageEnvirUnusualSitePercent of the cases: \eval copies the fields of the
list or data frame and creates bindings for them in a new environment. This
pattern is used to evaluate formulas which can directly refer to the fields of
the data. The \c{envir} argument can also be a number $n$. It means that the
environment in which the expressions is evaluated will be the result of
\c{sys.call(n)} where $n$ refers to the $n$-th stack frame.
